A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\citet{buckley_1942} in 1942 derived the Buckley-Leverett equation, an analytical (albeit simplified) two phase flow equation. The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation. The equation is referred to as "simplified" because of the assumptions made while deriving it, some of which were ignored in this work. Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities. Additionally, the permeability field in each block is heterogeneous. However, the general validation test or expectation from Buckley-Leverett's influence on this work, is that, the injected fluid saturation in $K1$ and $K2$ is expected to have a piston-shape front within those blocks, subject some inconsistency at the boundary between the two blocks, and also within the blocks due to the heterogeneity.

\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were somewhat replicated here for the simulations. Therefore, the work of \citet{dawe_2008} can be used to validate the resulting simulations from this work. In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$. Additionally, the cross-flow from $K1$ to $K4$ is well represented in the simulations.

Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases. In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)). Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.

>>>>

\citet{buckley_1942} in 1942 derived the Buckley-Leverett equation, an analytical (albeit simplified) two phase flow equation. The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation. The equation is referred to as ``simplified" because of the assumptions made while deriving it, some of which were ignored in this work. Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities. Additionally, the permeability field in each block is heterogeneous. However, the general validation test or expectation from Buckley-Leverett's influence on this work, is that, the injected fluid saturation in $K1$ and $K2$ is expected to have a piston-shape front within those blocks, subject some inconsistency at the boundary between the two blocks, and also within the blocks due to the heterogeneity.

\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were replicated here for the simulations. Therefore, the work of \citet{dawe_2008} can be used to qualitatively validate the resulting simulations from this work. In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$. Additionally, the cross-flow from $K1$ to $K4$ is well represented in the simulations.

Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases. In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}a-b, even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}c show that the fluid experiences a resistance to flow at the interface between $K1$ and $K3$ (due to lower permeability at $K2$ and $K3$) which encourages the flow into $K4$ (\ie bottom-right block, Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}d-e). Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
